---
title: "CWAS-SCA Bootstrap Results"
author: "Zarrar"
date: "May 29, 2015"
output: html_document
---

# Background

For each subject and each condition, I computed the connectivity between every pair of parcels (658) in the brain. Then across subjects, I computed the difference between the connectivity between conditions and calculated significance via a paired t-test. To summarize the results, at each parcel, I took the total number of connections between that parcel and every other parcel that were significant. I do this once for Bio < Phys contrast and another time for the Phys > Bio contrast. I found a region in the left vATL that had the largest number of connections that were significantly different between condtions.

To get estimates of the robustness of the left vATL connectivity changes relative to other regions, I did a bootstrap analysis. I randomly took a set of 10 subjects from my total of 16 and re-ran the above analysis. The goal was to see (a) how often the left vATL was on top in terms of # of significant connections that differ between conditions and (b) the stability of the specific seed-based map of the vATL with every other parcel across bootstrap resamples.

# Setup

```{r packages}
library(bigmemory)
library(grid)
library(ggplot2)
library(RColorBrewer)
```

## Load the Data

Let's load things up.

```{r load}
runtype   <- "Questions"
region    <- "parcels_group_localizer_n0658"
basedir   <- "/mnt/nfs/psych/faceMemoryMRI"
grpdir    <- file.path(basedir, "analysis/groups")
indir     <- file.path(grpdir, runtype, "cmaps", sprintf("ts_%s_bootstrap+perms.sca", region))

vatl.ranks<- as.numeric(read.table(file.path(indir, "bootstrap_vatl_ranks.txt"))[,1])

vatl.maps <- attach.big.matrix(file.path(indir, "bootstrap_vatl_maps.desc")) # regions x resamps
vatl.maps <- as.matrix(vatl.maps)
```

## Plotting Theme

```{r theme}
fte_theme <- function() {
  # Colors
  color.background = "#F0F0F0"
  color.grid.major = "#D0D0D0"
  color.axis.text = "#535353"
  color.axis.title = "#535353"
  color.title = "#3C3C3C"
  
  # Begin construction of chart
  theme_bw() +
    
  # Set the entire chart region to a light gray color
  theme(panel.background=element_rect(fill=color.background, color=color.background)) +
  theme(plot.background=element_rect(fill=color.background, color=color.background)) +
  theme(panel.border=element_rect(color=color.background)) +
  
  # Format the grid
  theme(panel.grid.major=element_line(color=color.grid.major,size=.75)) +
  theme(panel.grid.minor=element_blank()) +
  theme(axis.ticks=element_blank()) +
  
  # Format the legend, but hide by default
  theme(legend.position="none") +
  theme(legend.background = element_rect(fill=color.background)) +
  theme(legend.text = element_text(size=11,color=color.axis.title)) +
  
  # Set title and axis labels, and format these and tick marks
  theme(plot.title=element_text(face="bold",color=color.title,size=24,vjust=2)) + #hjust=-0.08
  theme(axis.text.x=element_text(face="bold",size=17,color=color.axis.text)) +
  theme(axis.text.y=element_text(face="bold",size=17,color=color.axis.text)) +
  theme(axis.title.x=element_text(face="bold",size=18,color=color.axis.title, vjust=-.5)) +
  theme(axis.title.y=element_text(face="bold",size=18,color=color.axis.title, vjust=1.5)) +
  
  # Plot margins
  theme(plot.margin = unit(c(1, 1, .7, .7), "cm"))
}

cols <- brewer.pal(9, "Set1")
cols2 <- brewer.pal(8, "Dark2")[c(1,4,6)] # Questions, NoQuestions, and Overlap
```


# Plots

## Ranks

```{r ranks}
p <- ggplot(data.frame(x=vatl.ranks), aes(x=x)) +
      geom_histogram(binwidth=5, fill=cols2[1]) + 
      xlim(0,135) + 
      xlab("Rank of vATL Parcel Connectivity") + ylab("Number of Bootstrap Samples") + 
      geom_hline(yintercept=0,size=1.2,colour="#535353") +
      fte_theme() + 
      theme(axis.title.x=element_blank()) + 
      theme(axis.title.y=element_blank())
print(p)
# TODO: save!  
```

## Correlation Maps

```{r corr}
# Compute the correlation between the connectivity maps
cmat <- cor(vatl.maps, method="spearman")
df.cmat <- data.frame(x=cmat[lower.tri(cmat)])

# Plot
p <- ggplot(df.cmat, aes(x=x)) +
      geom_histogram(binwidth=0.02, fill=cols2[1]) + 
      xlim(0,1) + 
      xlab("Spearman Rho") + ylab("Number of Pairwise Bootstrap Samples") + 
      geom_hline(yintercept=0,size=1.2,colour="#535353") +
      fte_theme() + 
      theme(axis.title.x=element_blank()) + 
      theme(axis.title.y=element_blank())
print(p)
```

```{r dice}
# Compute the dice coefficient amongst the significant results
dice <- function(a,b) (2*sum(a&b))/sum(a+b)
dice.mat <- function(a, b=a, z=0) {
    xa <- a > z; xb <- b > z
    mat <- matrix(1, ncol(xa), ncol(xb))
    inds <- expand.grid(list(a=1:ncol(xa), b=1:ncol(xb)))
    for (ri in 1:nrow(inds)) {
        i <- inds[ri,1]; j <- inds[ri,2]
        mat[j,i] <- mat[i,j] <- dice(xa[,i], xb[,j])
    }
    mat
}
dmat <- dice.mat(vatl.maps, z=1.645)
df.dmat <- data.frame(x=dmat[lower.tri(dmat)])

# Plot
p <- ggplot(df.dmat, aes(x=x)) +
      geom_histogram(binwidth=0.05, fill=cols2[1]) + 
      xlim(0,1) + 
      xlab("Dice Coefficient") + ylab("Number of Pairwise Bootstrap Samples") + 
      geom_hline(yintercept=0,size=1.2,colour="#535353") +
      fte_theme() + 
      theme(axis.title.x=element_blank()) + 
      theme(axis.title.y=element_blank())
print(p)
```



## Summary

This will give me the means and standard deviations I need for reporting. 

First the ranks

```{r summary-rank, results='hold'}
df <- data.frame(mean=mean(vatl.ranks), standard.deviation=sd(vatl.ranks))
print(df)
print(summary(vatl.ranks))
```

Second the correlation.

```{r summary-corr, results='hold'}
df <- data.frame(mean=mean(df.cmat$x), standard.deviation=sd(df.cmat$x))
print(df)
print(summary(df.cmat$x))
```

Third the dice.

```{r summary-dice, results='hold'}
df <- data.frame(mean=mean(df.dmat$x), standard.deviation=sd(df.dmat$x))
print(df)
print(summary(df.dmat$x))
```
