---
title: "PPI of Face-Selective ROIs"
author: "Zarrar Shehzad"
date: "May 8, 2015"
output: html_document
---

```{r packages}
library(plyr)
library(corrplot)
library(RColorBrewer)
library(knitr)
library(ggplot2)
library(reshape)
```

# Setup

We start by setting some variables and loading in the data and EVs.

```{r setup, results='hold'}
setwd("~/Dropbox/Research/facemem/connpaper")

# Make sure to not have any progress when building
#prog <- "none"
prog <- "text"

# We want to select a subset of the extract ROIs for our analyses
subjects <- as.character(as.matrix(read.table("sublist_all.txt")))
runtypes <- c("Questions", "NoQuestions")
conds    <- c("bio", "phys")
# We want to select a subset of the extract ROIs for our analyses
snames   <- c("R OFA", "R FFA", "R vATL", 
              "L OFA", "L FFA", "L vATL")
srois    <- c(
  3, 1, 69,  # R OFA, R FFA, R vATL
  8, 2, 62   # L OFA, L FFA, L vATL
)

# Load all the time-series data and select the relevant ROIs
tsdir <- "~/Dropbox/Research/facemem/data/ts"

# <= I predict I will read in all the time-series (only those I want) into a large array
# => no output needs to be list due to different ts length
# in 2min
cat("read in time-series\n")
tsdat <- llply(runtypes, function(runtype) {
  cat("Runtype:", runtype, "\n")
  ret <- llply(subjects, function(subject) {
    infile <- sprintf("%s/%s_%s_probatlas_peaks_ts.txt", tsdir, subject, runtype)
    sdat <- read.table(infile)
    sdat <- sdat[,srois]
    colnames(sdat) <- snames
    sdat
  }, .progress=prog)
  names(ret) <- subjects
  ret
})
names(tsdat) <- runtypes

# EVs
evdir <- "~/Dropbox/Research/facemem/connpaper/data/evs"
evinds <- 5:17
evnames <- c("bio", "phys", 
             "roll", "pitch", "yaw", "dS", "dL", "dP", 
             "comp1", "comp2", "comp3", "comp4", "comp5")

# <= Predict that will read in each file and format it for the desired columns
# <= so get a list of matrices with EVs
# => yup took 10mins
cat("Read in EVs\n")
evdat <- llply(runtypes, function(runtype) {
  cat("Runtype:", runtype, "\n")
  ret <- llply(subjects, function(subject) {
    #cat("-", subject, "\n")
    infile <- sprintf("%s/xmat_%s_%s_task+compcor+mc.1D", evdir, subject, runtype)
    edat <- read.table(infile)
    if (subject == "tb9555") {
      edat <- edat[,evinds-1] # cuz this subject has 3 runs
    } else {
      edat <- edat[,evinds]
    }    
    colnames(edat) <- evnames
    edat
  }, .progress=prog)
  names(ret) <- subjects
  ret
})
names(evdat) <- runtypes
```

Wow that was a process.

# PPI

In computing our interaction term, we will want to center the task regressors 
and demean the ROI time-series (as per the FSL instructions).

```{r}
ppi.center <- function(x) x - (max(x) - min(x))/2
ppi.demean <- function(x) x - mean(x)
```

## Sample Subject

Ok we want to now compute the PPI. Let's try this first for one subject. The PPI
model will include the task regressors, ROI time-series, and nuisance regressors.

```{r}
runtype  <- "Questions"
subject  <- "tb9226"
roi      <- "R OFA"

# The seed here refers to an ROI that is predicted the other ROIs
# It is in the model as the EVs and is predicted the Y/data.
ppi.res <- laply(runtypes, function(runtype) {
  laply(subjects, function(subject) {
    laply(snames, function(roi) {
      evs <- evdat[[runtype]][[subject]]
      rois <- tsdat[[runtype]][[subject]]
      evs <- cbind(evs[,1:2], roi = rois[[roi]],
                   bioXroi = ppi.center(evs[,1]) * ppi.demean(rois[[roi]]), 
                   physXroi = ppi.center(evs[,2]) * ppi.demean(rois[[roi]]), 
                   evs[,3:ncol(evs)])
      
      fit        <- lm(as.matrix(rois) ~ as.matrix(evs))
      bio.betas  <- fit$coefficients[5,]
      phys.betas <- fit$coefficients[6,]
      
      #tmp <- summary(fit)
      #bio.ts <- sapply(tmp, function(x) x$coefficients[5,3])
      #phys.ts <- sapply(tmp, function(x) x$coefficients[6,3])
      
      rbind(bio=bio.betas, phys=phys.betas)
    })
  }, .progress=prog)
})
dimnames(ppi.res) <- list(runtype=runtypes, subject=subjects, seed=snames, 
                          condition=conds, target=snames)
```

The results appear to suggest nothing in line with our hypotheses.
[need to think over this a bit. don't make an immediate decision change.]

```{r}
ppi.ts <- aaply(ppi.res, c(1,3,5), function(x) {
  t.test(x[,1], x[,2], paired=T)$statistic
})
ppi.sig <- aaply(ppi.res, c(1,3,5), function(x) {
  wilcox.test(x[,1], x[,2], paired=T)$p.value
})
round(ppi.ts[1,,], 2)
round(ppi.sig[1,,], 3)
# 1 = p < 0.1 and 2 = p < 0.05
(ppi.sig[1,,]<0.1) + (ppi.sig[1,,]<0.05)
```

TODO: try to run this all without the compcor regressers.

```{r}
# The seed here refers to an ROI that is predicted the other ROIs
# It is in the model as the EVs and is predicted the Y/data.
ppi.res <- laply(runtypes, function(runtype) {
  laply(subjects, function(subject) {
    laply(snames, function(roi) {
      evs <- evdat[[runtype]][[subject]]
      rois <- tsdat[[runtype]][[subject]]
      evs <- cbind(evs[,1:2], roi = rois[[roi]],
                   bioXroi = ppi.center(evs[,1]) * ppi.demean(rois[[roi]]), 
                   physXroi = ppi.center(evs[,2]) * ppi.demean(rois[[roi]]), 
                   evs[,3:(3+6)])
      
      fit        <- lm(as.matrix(rois) ~ as.matrix(evs))
      bio.betas  <- fit$coefficients[5,]
      phys.betas <- fit$coefficients[6,]
      
      rbind(bio=bio.betas, phys=phys.betas)
    })
  }, .progress=prog)
})
dimnames(ppi.res) <- list(runtype=runtypes, subject=subjects, seed=snames, 
                          condition=conds, target=snames)

```

```{r}
ppi.ts <- aaply(ppi.res, c(1,3,5), function(x) {
  t.test(x[,1], x[,2], paired=T)$statistic
})
ppi.sig <- aaply(ppi.res, c(1,3,5), function(x) {
  wilcox.test(x[,1], x[,2], paired=T)$p.value
})
round(ppi.ts[1,,], 2)
round(ppi.sig[1,,], 3)
# 1 = p < 0.1 and 2 = p < 0.05
(ppi.sig[1,,]<0.1) + (ppi.sig[1,,]<0.05)
```
